A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-07-16 faculty.tex
services

\subsection{Internal Funding}
These are funds from your university, city, or state (e.g., Virginia has the CCI program that provide ``seed'' grants for researchers from universities in Virginia).  Also, your ``startup'' package is also an internal funding to kickstart your research. These funding are less competitive than NSF, but they are also less prestigious (e.g., they aren't much and usually don't count as much for tenure).  However, they are good sources of funding to get preliminary results and later apply for traditional grants (and many internal funding programs explicitly encourage this).

@@

\paragraph{Personal Experiences}

@@

\appendix
\chapter{NSF Panel Reviews}

>>>>

\subsection{Internal Funding}
These are funds from your university, city, or state (e.g., Virginia has the CCI program that provide ``seed'' grants for researchers from universities in Virginia).  Your ``startup'' package is also be considered as a large funding from an internal source (your university) to kickstart your research. These funding are less competitive than NSF, but they are also less prestigious (e.g., they aren't much and usually don't count as much for tenure).  However, they are good sources of funding to get preliminary results and later apply for traditional grants (and many internal funding programs explicitly encourage this).

@@

\paragraph{Personal Experiences}
As with most tenure track professors, I focus mostly on NSF grants and most of my funding comes from NSF.  I only have one grant from Army Research Office (ARO) in which I am a co-PI and didn't have to write the proposal. I have tried to get other DoD funding, but without much success, I found that DoD program managers are very picky and often have their own agenda.  I have also received internal funding from my university and industrial gifts from Amazon,and Facebook.  I have found that industrial gifts are the best kind of funding, as they are unrestricted and have no associated timeline by when you should spend them.  They are also highly competitive and prestigious, and are a great way to get funding for your research.

@@

\appendix
\chapter{NSF Panel Reviews}
\chapter{Issues}

\section{Change in Departmental Leadership. Moving from UNL to GMU}

I joined UNL in 2016 and was very happy there until 2020, which is when the dept. changed its leadership and organization and lead to my decision to be on the job market again.

I do not want to get into details but below summarizes several things that happened

\begin{itemize}
\item 2019: four senior professors (in SE) left.  One of these 4 had became the chair of the dept and then left just after 2 months.  
\item 2020:  an even split among the faculty on moving to completely to the College of Engr.   Multiple senior people warn about this decision.  The new chair candidate only agrees to accept the job if the faculty moved to CoE, putting pressure on the move.
\item Salary inversion:  new chair offers new AP salary that is much higher than current AP, leading to jokes that current AP should just reapply to UNL.  This became a serious issue and many people at UNL use this as a reason on why they move.

\end{itemize}

Note that even after leaving Lincoln, my family and I still have a soft spot for the city and its people.  It was a great place to live and raise a family, but unfortunately not a good place to work for me.
